analysis

### 2020-06-05 analysis.Rmd
did something

### Prepare environment
```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(bipartite)
library(mgcv)
library(mgcViz)
#library(lme4)
#library(lmerTest)
install.packages("taxize")
library(taxize)
library(tidyverse)
library(lubridate)
library(GGally)
```

@@

fl_survey_elev_genus <- survey %>%
  filter(flower.cover > 0) %>%
  group_by(site, genus) %>%
  summarize(abund = sum(flower.cover)) %>%
  left_join(site_data) %>%
  group_by(genus) %>%
  mutate(elev.floor = min(elev.mean),
         elev.ceiling = max(elev.mean),
         elev.range = elev.ceiling - elev.floor,
         elev.med = elev.floor + ((elev.ceiling - elev.floor)/2),
         sites = length(unique(site)))

@@

ggplot(filter(fl_survey_elev, sites > 0), 
       aes(reorder(plant.sp, elev.med), elev.mean)) +
  geom_line(size = 1, color = "gray60") +
  geom_point(alpha = 0.5) +
  theme_light(14) +
  theme(axis.text.x = element_blank()) +
  xlab("Plant species") +
  ylab("Elevation")

ggplot(filter(fl_survey_elev_genus, sites > 0), 
       aes(reorder(genus, elev.med), elev.mean)) +
  geom_line(size = 1, color = "gray60") +
  geom_point(alpha = 0.5) +
  theme_light(10) +
  #theme(axis.text.x = element_blank()) +
  xlab("Plant genus") +
  ylab("Elevation") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

ggplot(abund_div, aes(elev.mean, fl.rich)) +
  geom_point(alpha = 0.5, aes(color = year)) +
  geom_smooth(color = "black", linetype = "dashed", size = 0.75) +
  theme_light(16) +
  xlab("Elevation") +
  ylab("Floral abundance")

@@

fl_abund_yday.vis <- getViz(fl_abund_yday)
check.gamViz(fl_abund_yday.vis)
summary(fl_abund_yday.vis)
plot(sm(fl_abund_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance 2010 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(fl_abund_yday.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance 2011 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(fl_abund_yday.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL abundance 2012 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

@@

plot(fl_abund_gdd.vis, allTerms = TRUE) +
  ggtitle("FL abundance (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
```

##### Floral richness
```{r eval=FALSE, include=FALSE}
fl_rich_yday <- gam(fl.rich ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

fl_rich_yday.vis <- getViz(fl_rich_yday)
check.gamViz(fl_rich_yday.vis)
summary(fl_rich_yday.vis)
plot(sm(fl_rich_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL richness 2010 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(fl_rich_yday.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL richness 2011 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(fl_rich_yday.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("FL richness 2012 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

@@

bb_abund_yday.vis <- getViz(bb_abund_yday)
check.gamViz(bb_abund_yday.vis)
summary(bb_abund_yday.vis)
plot(sm(bb_abund_yday.vis, 1)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("bb abundance 2010 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(bb_abund_yday.vis, 2)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("bb abundance 2011 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")
plot(sm(bb_abund_yday.vis, 3)) +
  l_fitRaster() +
  l_fitContour() +
  l_points() +
  ggtitle("bb abundance 2012 (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

@@

plot(bb_abund_gdd.vis, allTerms = TRUE) +
  ggtitle("BB abundance (gdd)") +
  xlab("Day of year") +
  ylab("Elevation")
```

>>>>

### Prepare environment
```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(bipartite)
library(mgcv)
library(mgcViz)
#library(lme4)
#library(lmerTest)
library(taxize)
library(tidyverse)
library(lubridate)
library(GGally)
```

@@

fl_survey_elev_family <- survey %>%
  filter(flower.cover > 0) %>%
  group_by(site, plant.family) %>%
  summarize(abund = sum(flower.cover)) %>%
  left_join(site_data) %>%
  group_by(plant.family) %>%
  mutate(elev.floor = min(elev.mean),
         elev.ceiling = max(elev.mean),
         elev.range = elev.ceiling - elev.floor,
         elev.med = elev.floor + ((elev.ceiling - elev.floor)/2),
         sites = length(unique(site)))

@@

ggplot(filter(fl_survey_elev, sites > 0), 
       aes(reorder(plant.sp, elev.ceiling), elev.mean)) +
  geom_line(size = 1, color = "gray60") +
  geom_point(alpha = 0.5) +
  theme_light(14) +
  theme(axis.text.x = element_blank()) +
  xlab("Plant species") +
  ylab("Elevation")

ggplot(filter(fl_survey_elev_family, sites > 0), 
       aes(reorder(plant.family, elev.med), elev.mean)) +
  geom_line(size = 1, color = "gray60") +
  geom_point(alpha = 0.5) +
  theme_light(10) +
  #theme(axis.text.x = element_blank()) +
  xlab("Plant family") +
  ylab("Elevation") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

ggplot(abund_div, aes(elev.mean, fl.rich)) +
  geom_point(alpha = 0.5, aes(color = year)) +
  geom_smooth(color = "black", linetype = "dashed", size = 0.75) +
  theme_light(16) +
  xlab("Elevation") +
  ylab("Floral richness")

@@

fl_abund_yday.vis <- getViz(fl_abund_yday)
check.gamViz(fl_abund_yday.vis)
summary(fl_abund_yday.vis)

plot(fl_abund_yday.vis, allTerms = TRUE) +
  ggtitle("FL abundance (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

@@

plot(fl_abund_gdd.vis, allTerms = TRUE) +
  ggtitle("FL abundance (gdd)") +
  xlab("GDD") +
  ylab("Elevation")
```

##### Floral richness -- since year does not seem to change the overall pattern (though perhaps the magnitude), I could use a simpler model, perhaps with year as a random intercept effect
```{r eval=FALSE, include=FALSE}
fl_rich_yday <- gam(fl.rich ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

fl_rich_yday.vis <- getViz(fl_rich_yday)
check.gamViz(fl_rich_yday.vis)
summary(fl_rich_yday.vis)

plot(fl_rich_yday.vis, allTerms = TRUE) +
  ggtitle("FL richness (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

@@

bb_abund_yday.vis <- getViz(bb_abund_yday)
check.gamViz(bb_abund_yday.vis)
summary(bb_abund_yday.vis)

plot(bb_abund_yday.vis, allTerms = TRUE) +
  ggtitle("BB abundance (yday)") +
  xlab("Day of year") +
  ylab("Elevation")

@@

plot(bb_abund_gdd.vis, allTerms = TRUE) +
  ggtitle("BB abundance (gdd)") +
  xlab("GDD") +
  ylab("Elevation")
```
